oREV item selection and analysis

### 2022-11-27 analysis/orev_item_selection.Rmd
finish determine size

```{r}
#determine_size <- tibble()

  for(j in 5:5){

  for (i in c(36:40)) {

    sub_dat <- irt_dat%>%filter(targetWord %in% sel)

    m1PL <- update(irt1_guess, newdata =sub_dat, chains = 6, cores = 6, threads = threading(8), backend = "cmdstanr")%>%add_criterion(c("loo"))
  	m3PL <- update(irt2PL, newdata =sub_dat, chains = 6, cores = 6, threads = threading(8), backend = "cmdstanr")%>%add_criterion(c("loo"))

  	comp <- loo_compare(m1PL, m3PL)%>%as_tibble(rownames = "model")%>%filter(model == "m1PL")%>%mutate(ratio = abs(elpd_diff)/(2*se_diff))

  	sub_dat_cor <- sub_dat%>%
  	  group_by(subjID)%>%
  	  summarise(mean_sub = mean(correct))

  	cor <- cor(sub_dat_cor$mean_sub,full$mean_full)

  	row <- tibble(size = i, 
           iter = j,
           elpd_diff = as.numeric(comp%>%pull(elpd_diff)),
           se_diff = as.numeric(comp%>%pull(se_diff)),
           ratio = as.numeric(comp%>%pull(ratio)),
           correlation = cor)

    determine_size <- bind_rows(determine_size, row)

    saveRDS(determine_size, "../saves/determine_size.rds")
  }

#saveRDS(determine_size, "../saves/determine_size.rds")

@@

determine_size%>%
  group_by(size)%>%
  summarise(n())

determine_size%>%
  group_by(size)%>%
  mutate(iter = 1:n())
```

>>>>

```{r}
# #determine_size <- tibble()
#   
#   for(j in 5:5){
#   
#   for (i in c(36:40)) {
#     
#     sim <- simulated_annealing_rasch(i)
#     
#     sel <- items[unlist(sim$best_subset) == TRUE]
#     
#     sub_dat <- irt_dat%>%filter(targetWord %in% sel)
#   
#     m1PL <- update(irt1_guess, newdata =sub_dat, chains = 6, cores = 6, threads = threading(8), backend = "cmdstanr")%>%add_criterion(c("loo"))
#   	m3PL <- update(irt2PL, newdata =sub_dat, chains = 6, cores = 6, threads = threading(8), backend = "cmdstanr")%>%add_criterion(c("loo")) 
#   	
#   	comp <- loo_compare(m1PL, m3PL)%>%as_tibble(rownames = "model")%>%filter(model == "m1PL")%>%mutate(ratio = abs(elpd_diff)/(2*se_diff))
#   	
#   	sub_dat_cor <- sub_dat%>%
#   	  group_by(subjID)%>%
#   	  summarise(mean_sub = mean(correct))
#   
#   	cor <- cor(sub_dat_cor$mean_sub,full$mean_full)
#   	
#   	row <- tibble(size = i, 
#            iter = j,
#            elpd_diff = as.numeric(comp%>%pull(elpd_diff)),
#            se_diff = as.numeric(comp%>%pull(se_diff)),
#            ratio = as.numeric(comp%>%pull(ratio)),
#            correlation = cor)
#     
#     determine_size <- bind_rows(determine_size, row)
#     
#     saveRDS(determine_size, "../saves/determine_size.rds")
#   }
#   
#   }
#   
# saveRDS(determine_size, "../saves/determine_size.rds")

@@
